---
title: "DATA 607: SQL and R(Lab2)"
author: "Subhalaxmi Rout"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This is by design a very open-ended assignment. In general, there’s no need here to ask “Can I…?” questions about your proposed approach. A variety of reasonable approaches are acceptable. You could for example access the SQL data directly from R, or you could create an intermediate .CSV file. I should be able to generate the SQL table(s) and data from your provided code—if you use a graphical user interface to create and populate tables, it should have a mechanism to generate corresponding SQL code.

## install required packages
#```{r setup, include=FALSE }
#install.packages("RMySQL")
#install.packages("readxl")
#install.packages('tinytex')
#tinytex::install_tinytex()
```

## Load Libraries
```{r}
library(RMySQL)
library(ggplot2)
```
## Create connection and fetch table from MySQL

```{r}
db_user <- 'root'
db_password <- 'root'
db_name <- 'movie'
db_host <- 'localhost'
db_port <- 3306
mydb <- dbConnect(MySQL(), user = db_user, password = db_password, dbname = db_name, host = db_host, port = db_port)
dbListTables(mydb)
dbReadTable(mydb, "movies")

```
## Apply condition "IFNULL", this replace NULL value to 'NA'
```{r}
sql <- "SELECT 
     m.title as MovieTitle, IFNULL(r.rating, 'NA') AS Rating
 FROM
 Movies m
 left JOIN
 rating r ON m.movie_id = r.movie_id
 where r.rating is not null";
result <- dbGetQuery(mydb, sql);
knitr::kable(
  head(result),
  caption = "dbGetQuery result set [head]"
)
```

## Draw bar chart show movie name with rating

```{r eval=TRUE, fig.width=10}
movies_ratings_df <- as.data.frame(result)
show(movies_ratings_df)
height <- as.numeric(movies_ratings_df$Rating)
names.arg <- movies_ratings_df$MovieTitle

my_plot <- ggplot(movies_ratings_df, aes(x=MovieTitle, y=Rating)) +geom_col(fill="navy")+theme_bw()
print(my_plot)
```
## Using {sql, eval=FALSE} markdown to only display SQL
``` {sql, eval=FALSE}
CREATE DATABASE movie;
USE movie;
DROP TABLE IF EXISTS movies;
DROP TABLE IF EXISTS rating;
/* Create movie table */
CREATE TABLE movies (
    movie_id INTEGER NOT NULL PRIMARY KEY,
    title VARCHAR(60) NOT NULL UNIQUE KEY
);
/* Insert values to movies table */
INSERT INTO movies (movie_id,title)
VALUES  (1, "Guardians of the Galaxy 2"),
        (2, "Wonder Woman"),
        (3, "Star Wars The Last Jedi"),
        (4, "Thor Ragnarok"),
        (5, "Blade Runner 2049"),
        (6, "Spider Man Homecoming");
/* Create rating table */
CREATE TABLE rating (
    rating_id INTEGER NOT NULL PRIMARY KEY,
    movie_id INTEGER,
    rating VARCHAR(60) UNIQUE KEY);

/* Insert values to movies table */
insert into rating (movie_id,rating_id,rating) 
values (1,1,4),
(2,2,3),
(3,3,5),
(4,4,2),
(5,5,4);

```


